% !TeX root=main.tex
% در این فایل، عنوان پایان‌نامه، مشخصات خود و چکیده پایان‌نامه را به انگلیسی، وارد کنید.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\baselineskip=.6cm
\begin{latin}
\latinuniversity{University of Tehran}
\latinfaculty{Faculty of Science\\ Department of Physics}
\latinsubject{Physics}
\latinfield{Gravitation and cosmology}
\latintitle{Black hole mimickers}
\firstlatinsupervisor{ِProf. Fatimah Shojai Baghini}
%\secondlatinsupervisor{Second Supervisor}
%\firstlatinadvisor{First Advisor}
%\secondlatinadvisor{Second Advisor}
\latinname{Armin}
\latinsurname{Sadeghi}
\latinthesisdate{Shahrivar-1404}
\latinkeywords{Regular black holes, Singularity, Ultracompact object, Surface gravity, Horizon, Black hole thermodynamics, Photon sphere, Shadow, Gauss-Bonnet gravity}
\en-abstract{
Black hole models, despite their remarkable successes, raise fundamental questions about the nature of spacetime, horizons, and singularities. The presence of singularities inside black holes suggests a theoretical breakdown that must be resolved. Black hole mimickers have been proposed as alternative candidates. Among the possible scenarios for addressing singularities, regular black holes and horizon-less ultra-compact stars have attracted attention. The former possess at least an outer and an inner horizon but lack a singular core. The latter are configurations without horizons and the stellar surface lies within the photon sphere. 
These two categories are the main examples of black hole mimickers. They are non-singular objects that cannot necessarily be distinguished from black holes through observation. They also avoid the challenges associated with black holes. 
Observations of massive objects such as supermassive black holes are limited to shadow measurements and gravitational waves. Recent advances in gravitational wave astronomy and horizon-scale electromagnetic imaging have opened new pathways to test these models. These advances have made the study of black holes and their mimicker models, an important topic. 
This thesis focuses on regular black holes  as a class of mimicker models and examines their formation through stellar collapse.
 We first examine the gravitational collapse leading to well-known  Bardeen and Hayward regular black holes.  Next, we generalize this scenario to a class of regular black holes with a de Sitter core. The Bardeen and Hayward solutions are two special cases of this class. Then, we study the dynamics of horizons during the collapse.
Additionally, we also analyze the collapse scenario for a regular black hole metric in four-dimensional Einstein–Gauss–Bonnet gravity to determine  whether this metric is truly regular and whether it can effectively serve as a mimicker. Furthermore, we study the surface gravity of collapsing stars that form regular black holes. We  extend this class of regular black holes to higher dimensions, introduce their energy–momentum tensor, analyze their photon spheres and shadows, and compare them with observations. Finally, we explore photon spheres, shadow, thermodynamics, entropy, heat capacity, and stability of this class of regular black holes.
}
\latinfirstPage
\end{latin}
